\begin{frame}[fragile]
\frametitle{Program branching, functionality switching}
  \begin{itemize}
    \item Graphics application contains a lot of different effects (bump mapping, shadows, paralax mapping, ...)
    \item Different effects require different shaders.
    \item Functionality switching can be performed on different levels.
    \item Switching program path using uniform variable.
    \item Subroutines switching
    \item Shader program pipelines switching
    \item Shader program switching
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Functionality switching - uniformn variables}
  The fastest functionality switch can be performed directly inside shader.
  However, there is per-invocation overhead.
  For example, vertex shader has to evaluate condition for every vertex (thread divergence).
    {\scriptsize
    \begin{minted}[frame=lines]{glsl}
#version 430
uniform uint method;
void main(){
  switch(method){
    case 1:
      normalMapping(...);
      break;
    case 2:
      paralaxMapping(...);
      break;
    case 3:
      ...
  }
}
    \end{minted}
    }
\end{frame}

\begin{frame}[fragile]
\frametitle{Functionality switching - subroutines}
  It is the second fastest functionality switch. It is function pointer switching.
    {\tiny
    \begin{minted}[frame=lines]{glsl}
#version 440

layout(location=0)out vec4 fColor;

subroutine vec4 getColorSubroutine();
subroutine vec4 rotateColorSubroutine(vec4);

subroutine (getColorSubroutine) vec4 redColor(){return vec4(1,0,0,1);}
subroutine (getColorSubroutine) vec4 greenColor(){return vec4(0,1,0,1);}

subroutine (rotateColorSubroutine) vec4 rotate1Left (vec4 c){return c.yzwx;}
subroutine (rotateColorSubroutine) vec4 rotate2Left (vec4 c){return c.zwxy;}
subroutine (rotateColorSubroutine) vec4 rotate3Left (vec4 c){return c.wxyz;}
subroutine (rotateColorSubroutine) vec4 reverse     (vec4 c){return c.wzyx;}

subroutine uniform getColorSubroutine    getColor;//fce pointer
subroutine uniform rotateColorSubroutine rotateColor[3];//array of fce pointers

uniform uint rotateIndex=0;

void main(){
  fColor=rotateColor[rotateIndex](getColor());
}
    \end{minted}
    }
\end{frame}

\begin{frame}[fragile]
\frametitle{Functionality switching - subroutines}
    {\tiny
    \begin{minted}[frame=lines]{c++}
//all subroutines
GLuint sl0=glGetSubroutineIndex(program,GL_FRAGMENT_SHADER,"redColor");
GLuint sl1=glGetSubroutineIndex(program,GL_FRAGMENT_SHADER,"greenColor");
GLuint sl2=glGetSubroutineIndex(program,GL_FRAGMENT_SHADER,"rotate1Left");
GLuint sl3=glGetSubroutineIndex(program,GL_FRAGMENT_SHADER,"rotate2Left");
GLuint sl4=glGetSubroutineIndex(program,GL_FRAGMENT_SHADER,"rotate3Left");
GLuint sl5=glGetSubroutineIndex(program,GL_FRAGMENT_SHADER,"reverse");

//uniform offsets for subroutines
GLuint sul0=glGetSubroutineUniformLocation(program,GL_FRAGMENT_SHADER,"getColor");
GLuint sul1=glGetSubroutineUniformLocation(program,GL_FRAGMENT_SHADER,"rotateColor");

glUseProgram(program);
//list of all slots for subroutines
GLuint sl[4];
sl[sul0+0]=sl1;
sl[sul1+0]=sl5;
sl[sul1+1]=sl2;
sl[sul1+2]=sl3;
glUniformSubroutinesuiv(GL_FRAGMENT_SHADER,4,sl);
    \end{minted}
    }
\end{frame}

\begin{frame}[fragile]
\frametitle{Functionality switching - pipelines}
\begin{itemize}
  \item Program pipelines can be used for shader stage switching (vertex,fragment,geometry,...).
  \item Inputs and outputs of stages has to match, they will not be checked.
  \item Pipeline switching is cheaper that program switching.
  \item It is usefull in situation where there is a lot of similar shader programs.
\end{itemize}
{\tiny
  \begin{minted}[frame=lines]{c++}
GLuint vs,gs,fs;
//This function creates shader program that contains only one shader stage.
vs=glCreateShaderProgramv(GL_VERTEX_SHADER,1,&vstext);
fs=glCreateShaderProgramv(GL_FRAGMENT_SHADER,1,&fstext);
//...

GLuint pipeline;
glGenPipelines(1,&pipeline);
glBindPipelines(pipeline);

//...
glUseProgramStages(pipeline,GL_VERTEX_SHADER_BIT,vs);
glUseProgramStages(pipeline,GL_GEOMETRY_SHADER_BIT,program);//select geometry shader from shader program
glUseProgramStages(pipeline,GL_FRAGMENT_SHADER_BIT,fs);
  \end{minted}
}
\end{frame}

